\bf Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-08-21 ProbabilisticCoherence.tex
Added keywords and acknowledgements

\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

@@

	\if1\blind
	{
		\title{\bf Probabilistic Forecasts in Hierarchical~Time~Series}
		\author{Puwasala Gamakumara\thanks{
				The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
			    Department of Econometrics and Business Statistics,\\
			    Monash University,\\ VIC 3800, Australia.\\
			    Email: Puwasala.Gamakumara@monash.edu \\
			    and \\
			    Anastasios Panagiotelis\\
			    Department of Econometrics and Business Statistics,\\
		    	Monash University,\\ VIC 3800, Australia.\\
			    Email: Anastasios.Panagiotelis@monash.edu \\
			    and \\
		        George Athanasopoulos\\
		        Department of Econometrics and Business Statistics,\\
		        Monash University,\\ VIC 3800, Australia.\\
		        Email: george.athanasopoulos@monash.edu \\
		        and \\
	            Rob J Hyndman\\
	            Department of Econometrics and Business Statistics,\\
	            Monash University,\\ VIC 3800, Australia.\\
	            Email: rob.hyndman@monash.edu \\}
		\maketitle
	} \fi

@@

\noindent%
{\it Keywords:}  3 to 6 keywords, that do not appear in the title
\vfill

>>>>

\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

@@

	\if1\blind
	{
		\title{\bf Probabilistic Forecasts in Hierarchical~Time~Series}
		        \author{Puwasala Gamakumara\thanks{
		        The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
			    Department of Econometrics and Business Statistics,\\
			    Monash University,\\ VIC 3800, Australia.\\
			    Email: Puwasala.Gamakumara@monash.edu \\
			    and \\
			    Anastasios Panagiotelis\\
			    Department of Econometrics and Business Statistics,\\
		    	Monash University,\\ VIC 3800, Australia.\\
			    Email: Anastasios.Panagiotelis@monash.edu \\
			    and \\
		        George Athanasopoulos\\
		        Department of Econometrics and Business Statistics,\\
		        Monash University,\\ VIC 3800, Australia.\\
		        Email: george.athanasopoulos@monash.edu \\
		        and \\
	            Rob J Hyndman\\
	            Department of Econometrics and Business Statistics,\\
	            Monash University,\\ VIC 3800, Australia.\\
	            Email: rob.hyndman@monash.edu \\}
		\maketitle
	} \fi

@@

\noindent%
{\it Keywords:}  Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
\vfill
